Download and Save the Actual Data on MCI

### 2024-01-23 script/01-download_data.qmd
Change the typo in scripts

```{r}
#### Preamble ####
# Purpose: Download and save the actual data on major crimes that reported in Toronto 
# from 2014 to 2023
# Author: Boxuan Yi
# Email: boxuan.yi@mail.utoronto.ca
# Date: 18 January 2024
# Prerequisites: Know where to get major crimes data.
# I will use MCI as an abbreviation of Major Crime Indicator
```

>>>>

```{r}
#### Preamble ####
# Acquire
# Purpose: Download and save the actual data on major crimes that reported in Toronto 
# from 2014 to 2023
# Author: Boxuan Yi
# Email: boxuan.yi@mail.utoronto.ca
# Date: 18 January 2024
# Prerequisites: Know where to get major crimes data.
# I will use MCI as an abbreviation of Major Crime Indicator
```
